Embedding to Reference t-SNE Space Adresses Batch Effects in Single-Cell Classification

### 2019-06-14 paper/tsne_embedding.tex
Minor correction and re-order references.

\begin{document}
%
\title{Embedding to Reference t-SNE Space Adresses Batch-Effects in Single-Cell Classification}
%
\titlerunning{t-SNE Embedding and Batch Effects}
%
\author{Pavlin G. Poli\v{c}ar\inst{1} \and
Martin Stra\v{z}ar\inst{1} \and
Bla\v{z} Zupan\inst{1,2}}
%
\authorrunning{P. G. Poli\v{c}ar, M. Stra\v{z}ar, and B. Zupan}
%
\institute{University of Ljubljana, SI-1000 Ljubljana, Slovenia 
\email{\{pavlin.policar,martin.strazar,blaz.zupan\}@fri.uni-lj.si}\\[2pt]
\and
Baylor College of Medicine, Houston, TX 77030, USA
}

@@

Current solutions to embedding the data from various data sources address the
batch effect problems up-front. The data is typically preprocessed and
transformed such that the batch effects are explicitly
removed. Recently proposed procedures for batch-effect removal include
canonical correlation analysis~\cite{cca} and mutual
nearest-neighbors~\cite{mnn,seurat}.
In these works, batch effects are deemed removed when cells from different sources exhibit good mixing in a t-SNE visualization.
The elimination of batch effects may require aggressive data
preprocessing which may blur the boundaries between cell types. Another problem
is also the inclusion of any new data, for which the entire data analysis
pipeline must be rerun, usually resulting in a different layout and clusters
that have little resemblance to original visualization and thus require
reinterpretation.

@@

\bibliographystyle{splncs04}
\bibliography{references}
\end{document}

>>>>

\begin{document}
%
\title{Embedding to Reference t-SNE Space Adresses Batch Effects in Single-Cell Classification}
%
\titlerunning{t-SNE Embedding and Batch Effects}
%
\author{Pavlin G. Poli\v{c}ar\inst{1} \and
Martin Stra\v{z}ar\inst{1} \and
Bla\v{z} Zupan\inst{1,2}}
%
\authorrunning{P. G. Poli\v{c}ar, M. Stra\v{z}ar, and B. Zupan}
%
\institute{University of Ljubljana, SI-1000 Ljubljana, Slovenia 
\email{\{pavlin.policar,martin.strazar,blaz.zupan\}@fri.uni-lj.si}\\[2pt]
\and
Baylor College of Medicine, Houston, TX 77030, USA
}

@@

Current solutions to embedding the data from various data sources address the
batch effect problems up-front. The data is typically preprocessed and
transformed such that the batch effects are explicitly
removed. Recently proposed procedures for batch effect removal include
canonical correlation analysis~\cite{cca} and mutual
nearest-neighbors~\cite{mnn,seurat}.
In these works, batch effects are deemed removed when cells from different sources exhibit good mixing in a t-SNE visualization.
The elimination of batch effects may require aggressive data
preprocessing which may blur the boundaries between cell types. Another problem
is also the inclusion of any new data, for which the entire data analysis
pipeline must be rerun, usually resulting in a different layout and clusters
that have little resemblance to original visualization and thus require
reinterpretation.

@@

% \bibliographystyle{splncs04}
\bibliographystyle{unsrt}
\bibliography{references}
\end{document}
